\chapter*{Resumen}
\thispagestyle{empty}

En este trabajo se presenta una optimizaci\'on computacional novedosa del filtro deceived non local means usando media m\'ovil y simetr\'ia en el pesado. Se realiza la evaluaci\'on de la optimizaci\'on propuesta con distintos enfoques para disminuir el costo computacional del filtro deceived non local means. Adem\'as, tambi\'en se comprueba el impacto de paralelizar los enfoques de optimizaci\'on, evaluando el tiempo de ejecuci\'on y la escalabilidad en una arquitectura many-core. El enfoque propuesto para la implementaci\'on secuencial alcanza una aceleraci\'on de $90$, mientras que su contraparte paralela alcanza un speedup de $665$ en una imagen de entrada de $1024\times1024$.

\bigskip

\textbf{Palabras clave:} \scriptKeywords

\clearpage
\chapter*{Abstract}
\thispagestyle{empty}

This work presents a novel computational optimization of the deceived non local means filter using moving average and symmetric weighting. Comprise an evaluation of the proposed optimization with different approaches to lower the computational cost of the deceived non local means filter. Furthermore, also assess the impact of parallelizing the different optimization approaches, evaluating the execution time and scalability in a many-core architecture. The proposed approach for the non-parallel implementation achieved a $90$ speedup, while its parallelized counterpart yielded a $665$ speedup with a $1024\times1024$ input image. 

\bigskip

\textbf{Keywords:} Non Local Means filter, Image Processing, Parallelization, Computational Cost, Optimization, Xeon Phi Knights Landing.

\cleardoublepage

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "main"
%%% End: 
